District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-15 paper/paper.tex

TODO: Finish this write up!
TODO: Add results! Also add ternary plot

@@

% Map Plot
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/02_map_plot_facet.png}
    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively. Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
\end{figure}

@@

% Dumbbell of type-specific cov change 00'-20'
% todo: Rewrite caption
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/05_change_00_20.png}
    \caption{\emph{Absolute difference, with associated errors, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region. Plots are split by circumcision type. Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.  }}
\end{figure}

>>>>

\todo{Finish this write up!}
\todo{Add results! Also add ternary plot}

@@

% Map Plot
\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]
    \includegraphics[width=1\linewidth]
    % {plots/02_map_plot_facet.png}
    {paper/plots/02_map_plot_facet.png}
    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively. Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
\end{figure}
\todo{
  - Use divergent colour palette for "% change", and different one for coverage
- Need to position colour bars under corresponding facets, rather than to the side
- Grey out countries with no type (done)
- reevaluate text size
}

@@

% Dumbbell of type-specific cov change 00'-20'
% todo: Rewrite caption
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/05_change_00_20.png}
    % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region. Plots are split by circumcision type. Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.  }}
    \caption{\emph{Absolute change in circumcision coverage between 2000 and 2020 for 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type. The countries below the horizontal black line are VMMC priority countries}}
\end{figure}
